---
title: "main-functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{main-functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(measlesr)
```

## Planned Functions for measlesr

### Function 1: `plot_monthly_cases()`

```{r}
plot_monthly_cases(cases_month, year = 2018, country = "Madagascar")
```

This should make a line plot showing the total number of measles cases for each month in a given year for a specified country. The x-axis will show months (Jan–Dec) and the y-axis will show total case counts.

---

### Function 2: `yearly_case_summary()`

```{r}
yearly_case_summary(cases_year, country = "Madagascar")
```

This should return a summary table showing the total measles cases per year for a given country, along with the year-over-year percentage change and a trend label (surging, stable, or declining).

---

### Function 3: `plot_detection_props()`

```{r}
plot_detection_props(cases_year, methods = c("Clinical", "Epi-Linked", "Lab Confirmed"), min_year = 2012)
```

This should make a stacked bar chart showing what proportion of total measles cases each year were identified by each detection method (clinical, epi-linked, or lab confirmed). The x-axis will show year and the y-axis will show proportion of total cases.
